ANGSD-wrapper: utilities for analyzing next generation sequencing data

### 2016-01-27 manuscript.tex
spectra

\begin{figure}
\centering
\includegraphics[width=0.8\linewidth]{figures/figure3big.pdf}
\caption{Summary statistics for {\it Zea mays}. Derived site frequency spectra for A. maize and B. teosinte. C. distribution of pairwise differences for maize (blue) and teosinte (orange). Pairwise diversity results are visualized separately from the interactive graphics and colors were added to A and B using a custom script.}
\label{fig:figure3}
\end{figure}
\jri{figure says "spectrum" should be plural}
As a demonstration of analyses in ANGSD-wrapper, we explore patterns of diversity in a single genomic region of domesticated maize and wild teosinte. 
We used a subset of the resequenced samples from the Maize HapMap2 project (Table \ref{tab:samples}) and calculated summary statistics using a 10Mb region on chromosome 10 \citep{chia2012maize}. 
The data are available at \url{https://figshare.com/articles/Example_Data_tar_bz2/2063442}. 
In the following we refer to methods listed in Table \ref{tab:methods} when describing analyses.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\linewidth]{figures/figure3big.pdf}
\caption{Summary statistics for {\it Zea mays}. Derived site frequency spectra for A. maize and B. teosinte. C. distribution of pairwise differences for maize (blue) and teosinte (orange). Pairwise diversity results are visualized separately from the interactive graphics and colors were added to A and B using a custom script.}
\label{fig:figure3}
\end{figure}
As a demonstration of analyses in ANGSD-wrapper, we explore patterns of diversity in a single genomic region of domesticated maize and wild teosinte. 
We used a subset of the resequenced samples from the Maize HapMap2 project (Table \ref{tab:samples}) and calculated summary statistics using a 10Mb region on chromosome 10 \citep{chia2012maize}. 
The data are available at \url{https://figshare.com/articles/Example_Data_tar_bz2/2063442}. 
In the following we refer to methods listed in Table \ref{tab:methods} when describing analyses.
